\speculake: Hiding Malware in Speculative Execution

### 2018-05-09 paper/implementation.tex
implementation pass

Our Turing implementation discovered that 4 repetitions is sufficient for the
real world to determine the correct value, as the ``hit rate'' for any one
iteration observing the correct value loaded in cache was over 80\%.

We implemented the 5 state Busy Beaver configuration which requires over 47
million steps to complete. We were able to verify that the speculative world
could correctly compute 20 thousand steps with no errors at a rate of 324
instructions per second.

@@

We demonstrate the speed that information can be decrypted via the speculative
world, and we vary the channel width of the side channel from 1 to 12 bit to
measure its performance. At low channel width, reading from the cache side
channel requires timing reads from only 2 locations, while at 12-bits, the side
channel requires reading $2^{12}$ locations. On the flip side, there is a fixed
overhead per iteration that favors increased channel width to maximize
bandwidth. As shown in Figure~\ref{fig:spec_bandwidth}, 8 bits is the optimal
side channel width, allowing us to decrypt over 5,000 bits per second (625
Bytes/sec).

@@

In SPASM we have implemented multiple example programs that can be run as
encrypted binaries in an \speculake payload: First, a \textit{HelloWorld}
program that prints to \texttt{stdout}. Next, a \texttt{FizzBuzz} program that
demonstrates control flow and arithmetic operations while printing to stdout.
And finally, a \textit{ReverseShell} program that opens and connects to a socket
before  duplicating I/O file descriptors and executing a local shell. Details of
the SPASM instruction set can be found in Appendix~\ref{appendix:spasm}.

Expected performance for a given SPASM binary will vary given multiple factors, 
the most important of which is the \texttt{Flush+Reload} redundancy. This can be tuned
based on the specific trigger, as it is used to establish confidence that a signal 
has been identified in the indicess returned from the "speculative world". 
%Thus accomplishing a task using SPASM generally equates to:

>>>>

Our Turing implementation discovered that 10 repetitions is sufficient for the
real world to determine the correct value, as the ``hit rate'' for any one
iteration observing the correct value loaded in cache was over 80\%.

We implemented the 5 state Busy Beaver configuration which requires over 47
million steps to complete. Figure~\ref{fig:turing_success} shows the
capabilities of our Turing implementation. We were able to verify that the
speculative world could correctly compute a million instructions with no errors
at a rate of 324 instructions per second.

@@

We demonstrate the speed that information can be decrypted via the speculative
world, and we vary the channel width of the side channel from 1 to 12 bits to
measure its performance. At low channel width, reading from the cache side
channel requires timing reads from only 2 locations, while at 12-bits, the side
channel requires reading $2^{12}$ locations. On the other hand, there is a fixed
overhead per iteration that favors increased channel width to maximize
bandwidth. As shown in Figure~\ref{fig:spec_bandwidth}, 8 bits is the optimal
side channel width, allowing us to decrypt over 5,000 bits per second (625
Bytes/sec).

@@

In SPASM we have implemented multiple example programs that can be run as
encrypted binaries in an \speculake payload: First, a \textit{HelloWorld}
program that prints to \texttt{stdout}. Next, a \texttt{FizzBuzz} program that
demonstrates control flow and arithmetic operations while printing to stdout.
And finally, a \textit{ReverseShell} program that opens and connects to a socket
before  duplicating I/O file descriptors and executing a local shell. Details of
the SPASM instruction set can be found in Appendix~\ref{appendix:spasm}. Figure~\ref{fig:spasm_model} details the high-level flow of a SPASM payload.

Expected performance for a given SPASM binary will vary given multiple factors,
the most important of which is the \texttt{Flush+Reload} redundancy. This can be
tuned based on the specific trigger, as it is used to establish confidence that
a signal has been identified in the indices returned from the "speculative
world". 
%Thus accomplishing a task using SPASM generally equates to:
